\documentclass[a4paper,14pt]{article} 
% Этот шаблон документа разработан в 2014 году 
% Данилом Фёдоровых (danil@fedorovykh.ru) 
% для использования в курсе 
% «Документы и презентации в \LaTeX», записанном НИУ ВШЭ 
% для Coursera.org: http://coursera.org/course/latex . 
% Исходная версия шаблона —- 
% https://www.writelatex.com/coursera/latex/5.3 

% В этом документе преамбула 

%%% Работа с русским языком 
\usepackage{cmap} % поиск в PDF 
\usepackage{mathtext} % русские буквы в формулах 
\usepackage[T2A]{fontenc} % кодировка 
\usepackage[cp1251]{inputenc} % кодировка исходного текста 
\usepackage[english]{babel} % локализация и переносы 
\usepackage{indentfirst} 
\frenchspacing
\usepackage[shortlabels]{enumitem}

\renewcommand{\epsilon}{\ensuremath{\varepsilon}} 
\renewcommand{\phi}{\ensuremath{\varphi}} 
\renewcommand{\kappa}{\ensuremath{\varkappa}} 
\renewcommand{\le}{\ensuremath{\leqslant}} 
\renewcommand{\leq}{\ensuremath{\leqslant}} 
\renewcommand{\ge}{\ensuremath{\geqslant}} 
\renewcommand{\geq}{\ensuremath{\geqslant}} 
\renewcommand{\emptyset}{\varnothing} 


%%% Дополнительная работа с математикой 
\usepackage{amsmath,amsfonts,amssymb,amsthm,mathtools} % AMS 
\usepackage{icomma} % "Умная" запятая: $0,2$ —- число, $0, 2$ —- перечисление 

%% Номера формул 
%\mathtoolsset{showonlyrefs=true} % Показывать номера только у тех формул, на которые есть \eqref{} в тексте. 
%\usepackage{leqno} % Нумереация формул слева 

%% Свои команды 
\DeclareMathOperator{\sgn}{\mathop{sgn}}
\DeclareMathOperator*{\argmin}{arg\,min}

%% Перенос знаков в формулах (по Львовскому) 
\newcommand*{\hm}[1]{#1\nobreak\discretionary{} 
	{\hbox{$\mathsurround=0pt #1$}}{}} 

%%% Работа с картинками 
\usepackage{graphicx} % Для вставки рисунков 
\graphicspath{{images/}{images2/}} % папки с картинками 
\setlength\fboxsep{3pt} % Отступ рамки \fbox{} от рисунка 
\setlength\fboxrule{1pt} % Толщина линий рамки \fbox{} 
\usepackage{wrapfig} % Обтекание рисунков текстом 
\usepackage{float}

%%% Работа с таблицами 
\usepackage{array,tabularx,tabulary,booktabs} % Дополнительная работа с таблицами 
\usepackage{longtable} % Длинные таблицы 
\usepackage{multirow} % Слияние строк в таблице 

%%% Теоремы 
\theoremstyle{plain} % Это стиль по умолчанию, его можно не переопределять. 
\newtheorem{theorem}{Теорема}[section] 
\newtheorem{proposition}[theorem]{Утверждение}

\theoremstyle{definition} % "Определение" 
\newtheorem{corollary}{Следствие}[theorem] 
\newtheorem{problem}{Задача}[section] 

\theoremstyle{remark} % "Примечание" 
\newtheorem*{nonum}{Решение} 

%%% Программирование 
\usepackage{etoolbox} % логические операторы

%%% Страница 
\usepackage{extsizes} % Возможность сделать 14-й шрифт 
\usepackage{geometry} % Простой способ задавать поля 
\geometry{top=20mm} 
\geometry{bottom=25mm} 
\geometry{left=20mm} 
\geometry{right=20mm} 
% 
%\usepackage{fancyhdr} % Колонтитулы 
% \pagestyle{fancy} 
%\renewcommand{\headrulewidth}{0pt} % Толщина линейки, отчеркивающей верхний колонтитул 
% \lfoot{Нижний левый} 
% \rfoot{Нижний правый} 
% \rhead{Верхний правый} 
% \chead{Верхний в центре} 
% \lhead{Верхний левый} 
% \cfoot{Нижний в центре} % По умолчанию здесь номер страницы 

\usepackage{setspace} % Интерлиньяж 
\onehalfspacing % Интерлиньяж 1.5 
%\doublespacing % Интерлиньяж 2 
%\singlespacing % Интерлиньяж 1
\setlength{\parindent}{1cm}

\usepackage{lastpage} % Узнать, сколько всего страниц в документе. 

\usepackage{soul} % Модификаторы начертания 

\usepackage{hyperref} 
\usepackage[usenames,dvipsnames,svgnames,table,rgb]{xcolor} 
\hypersetup{ % Гиперссылки 
	unicode=true, % русские буквы в раздела PDF 
	pdftitle={Заголовок}, % Заголовок 
	pdfauthor={Автор}, % Автор 
	pdfsubject={Тема}, % Тема 
	pdfcreator={Создатель}, % Создатель 
	pdfproducer={Производитель}, % Производитель 
	pdfkeywords={keyword1} {key2} {key3}, % Ключевые слова 
	colorlinks=true, % false: ссылки в рамках; true: цветные ссылки 
	linkcolor=red, % внутренние ссылки 
	citecolor=black, % на библиографию 
	filecolor=magenta, % на файлы
	urlcolor=blue % на URL 
} 

\usepackage{csquotes} % Еще инструменты для ссылок 

%\usepackage[style=authoryear,maxcitenames=2,backend=biber,sorting=nty]{biblatex} 

\usepackage{multicol} % Несколько колонок 

\usepackage{tikz} % Работа с графикой 
\usepackage{pgfplots} 
\usepackage{pgfplotstable} 


\author
{Ilya Zharikov, Roman Isachenko, Artem Bochkarev} 
\title 
{Generative models for human activity recognition}
\date{}

\begin{document} 
\maketitle

\section*{Introduction}
This project is dedicated to multiclass classification of complex-structured objects (for which we don't have explicit features). 
The problem arises in many applications such as image recognition, signal processing or time series classification. 
We will focus on multiclass multivariate time series classification. 
In this setup time series are regarded as complex-structured objects without explicit feature description. 
This is reasonable because we can't operate with original features as time series might be of different size and not aligned \cite{geurts2001pattern}.

We investigate classification of accelerometer time series \cite{wang2014human}. The data is time series of acceleration from three axis, which is sensed by mobile phone or other portable device with accelerometer. 
The task is to predict the activity a person is performing. 
List of activities might include walking, running, sitting or walking up/down the stairs.

In general the problem of classifying complex-structured objects can be split in two distinctive procedures. 
First, we need to extract informative features, and then we use those features as input to some classifier to obtain final model. 
For simplicity, we assume that these two procedures can be built and analyzed separately. 
In our project we focused mainly on comparing different methods of feature generation \cite{karasikov24feature, ivkin}. 
Extracted features can be later used for building classifiers and feature selection algorithms.

The first approach for feature generation is calculating expertly defined functions of time series \cite{kwapisz2011activity}. 
These functions include average value, standard deviation, mean absolute deviation and distribution for each component. 
We consider this approach a baseline, as it is the simplest method we use.

We compare baseline with more sophisticated parametric feature generation methods. 
One of them is autoregressive model \cite{lukashin2003adaptive}. 
For each time series we build parametric model and use those parameters as features for classification. 
We also consider the model of singular spectrum analysis of time series \cite{hassani2007singular}. 
We use eigenvalues of trajectory matrix as features for building classifier.

In the first part of these report we give definitions and make problem statement. In the second part we describe all of the proposed approaches in more detail. 
Last, we make the experiment on real accelerometer datasets \cite{wisdm, usc}, compare all methods and give conclusions and recommendations for practical use.

\section*{Problem Statement}
Let $\mathcal{S}$ be a space of complex-structured objects, $Y$ is a finite set of class labels. 
Denote by $\mathfrak{D} = \{(s_i, y_i)\}_{i=1}^m$~-- given sample, where $s_i \in \mathcal{S}$ and $y_i \in Y$.

We consider the problem of recovering the function $f: \mathcal{S} \rightarrow Y$
\[
	y = f(s).
\]
Let $L(f, \mathfrak{D})$ be an error function which expresses the classification error of the function $f$ over the sample $\mathfrak{D}$. 
Our goal is to determine function $f^*$ which minimize the error
\begin{equation}
	f^* = \arg \min_{f} L(f, \mathfrak{D}).
	\label{eq::general_classification_task}
\end{equation}

We assume that the target function $f^*$ belongs to the class of functions composition $f = g \circ h$, where
\begin{itemize}
	\item 
	$h: \mathcal{S} \rightarrow H$ is a map from the original space $\mathcal{S}$ to the feature space $H \in \mathbb{R}^n$;
	\item 
	$g: H \times \Theta \rightarrow Y$ is a parametric map from feature space $H$ to the space of class labels $Y$. 
	The function $g$ is parametrized by a vector parameter $\theta \in \Theta$. 
\end{itemize}

The determining of the function $f^*$ is equivalent to determining the functions $h^*$ and  $g^*$.

In this paper we consider the following ways of generating the feature space~$H$:
\begin{itemize}
	\item 
	expert functions based on prior knowledge of the original objects. 
	For the time series analysis problem these functions are different statistics $\{h_i\}_{i=1}^n$ of given accelerations along each axis such as mean value, standard deviation and others. 
	The description $\mathbf{h}$ of the object $s$ is the value of these statistics on the object 
	\[
		\mathbf{h} = h(s) = (h_1(s), \dots, h_n(s)).
	\]
	\item 
	hypothesis of data generation. 
	In this case the features are the estimated parameters of the considered hypothesis. 
	Let $S(s, \mathbf{h}, \mathbf{\lambda})$ be the error function which specifies the hypothesis, e.g. one could define the function $S$ as negative log-likelihood function [to do link]. 
	The optimal parameters $\widehat{\mathbf{h}}$ for object $s$ is obtained by
	\begin{equation}
		\widehat{\mathbf{h}} = \arg \min_{\mathbf{h}} S( s, \mathbf{h}, \lambda).
		\label{eq::optimal_description}
	\end{equation}
	The parameter $\lambda$ is external structural parameter for the function $S$.
	The equation~\eqref{eq::optimal_description} determines the feature map $h:\mathcal{S} \rightarrow H$.
\end{itemize}

Given appropriate feature space $H$ and feature map $h$ we transform our original sample $\mathfrak{D} = \{s_i, y_i\}_{i=1}^m$ to the $\mathfrak{D}_H = \{\mathbf{h}_i, y_i\}_{i=1}^m$, where $\mathbf{h}_i = h(s_i)$. 
The function $g(\mathbf{h}, \theta)$ is defined by its parameters vector $\theta \in \Theta$. 
The optimal parameters~$\widehat{\theta}$ are given by
\[
	\widehat{\theta} = \arg \min_{\theta} L(g(\cdot, \theta), \mathfrak{D}_H),
\]
where $L(\cdot, \cdot)$ is an analogue of the function~\eqref{eq::general_classification_task}.

\bibliographystyle{unsrt}
\bibliography{ref.bib}
\end{document}